---
title: "Vignette Title"
author: "Vignette Author"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

The wifiparis project was undertaken by Amir Benmahjoub, Sacha Izadi and Alexandre Momeni for their R course at École Polytechnique. It originated from a ParisData dataset on free public wifi hotspot connexions in 2016. 

The dataset was subsequently cleaned and structured using several mapping files to form part of a new R package called "wifiparis". The package also includes spatial datasets of Parisian boroughs and individual wifi sites as well as filtering and visualisation functions. The "wifiparis" packages was then used as as the basis for a Shiny App. 

The objective of the project is to enables end users to explore the dataset freely and gather insights through different visualisations in this App. 


3 - doc d'utilisation de l'app
4 - (si on est chaud ) un ou deux insight

I hope this email finds you well. Amir, Sacha and I have been working on a ParisData dataset consisting of different data items collected via free public wifi hotspot connexions in 2016. We have cleaned and structured this dataset, created a package and published a Shiny app. Users will be able to explore the dataset freely and gather insights through our different visualisations. 
The Paris Wifi Projet 


Vignettes are long form documentation commonly included in packages. Because they are part of the distribution of the package, they need to be as compact as possible. The `html_vignette` output type provides a custom style sheet (and tweaks some options) to ensure that the resulting html is as small as possible. The `html_vignette` format:

- Never uses retina figures
- Has a smaller default figure size
- Uses a custom CSS stylesheet instead of the default Twitter Bootstrap style

## Vignette Info

Note the various macros within the `vignette` section of the metadata block above. These are required in order to instruct R how to build the vignette. Note that you should change the `title` field and the `\VignetteIndexEntry` to match the title of your vignette.

## Styles

The `html_vignette` template includes a basic CSS theme. To override this theme you can specify your own CSS in the document metadata as follows:

    output: 
      rmarkdown::html_vignette:
        css: mystyles.css

## Figures

The figure sizes have been customised so that you can easily put two images side-by-side. 

```{r, fig.show='hold'}
plot(1:10)
plot(10:1)
```

You can enable figure captions by `fig_caption: yes` in YAML:

    output:
      rmarkdown::html_vignette:
        fig_caption: yes

Then you can use the chunk option `fig.cap = "Your figure caption."` in **knitr**.

## More Examples

You can write math expressions, e.g. $Y = X\beta + \epsilon$, footnotes^[A footnote here.], and tables, e.g. using `knitr::kable()`.

```{r, echo=FALSE, results='asis'}
knitr::kable(head(mtcars, 10))
```

Also a quote using `>`:

> "He who gives up [code] safety for [code] speed deserves neither."
([via](https://twitter.com/hadleywickham/status/504368538874703872))
